Baseline Travel Survey Summary ITHIM-R

### 2021-04-22 code/producing_trips_rd/trip-summary.Rmd
Removed first table trip summary

---
title: "Trip Summary ITHIM-R"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

```
```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
(readxl::read_excel("C:/Users/danie/Documents/Daniel_Gil/Consultorias/2020/WorldBank/ITHIM-R/code/producing_trips_rd/Travel_survey_details.xlsx")
  ) %>% kbl() %>% kable_classic()

@@

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
trip <- read_csv("../../data/local/buenos_aires/buenos_aires_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Buenos_Aires <- value

trip <- read_csv("../../data/local/sao_paulo/sao_paulo_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Sao_Paulo <- value

trip <- read_csv("../../data/local/belo_horizonte/belo_horizonte_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Belo_Horizonte <- value

trip <- read_csv("../../data/local/mexico_city/mexico_city_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Mexico <- value

trip <- read_csv("../../data/local/bogota/bogota_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Bogota <- value

trip <- read_csv("../../data/local/santiago/santiago_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Santiago <- value

trip <- read_csv("../../data/local/vizag/vizag_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Visakhapatnam <- value

trip <- read_csv("../../data/local/delhi/delhi_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Delhi <- value

trip <- read_csv("../../data/local/bangalore/bangalore_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Bangalore <- value

trip <- read_csv("../../data/local/accra/accra_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Accra <- value

trip <- read_csv("../../data/local/cape_town/cape_town_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Cape_Town <- value

@@

>>>>

---
title: "Baseline Travel Survey Summary ITHIM-R"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

```
```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
# (readxl::read_excel("C:/Users/danie/Documents/Daniel_Gil/Consultorias/2020/WorldBank/ITHIM-R/code/producing_trips_rd/Travel_survey_details.xlsx")
#   ) %>% kbl() %>% kable_classic()

@@

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
trip_buenos_aires <- read_csv("../../data/local/buenos_aires/buenos_aires_trip.csv",
                 guess_max = 100000)
quality_check(trip_buenos_aires)
trip_summary$Buenos_Aires <- value

trip_sao_paulo <- read_csv("../../data/local/sao_paulo/sao_paulo_trip.csv",
                 guess_max = 100000)
quality_check(trip_sao_paulo)
trip_summary$Sao_Paulo <- value

# trip_belo_horizonte <- read_csv("../../data/local/belo_horizonte/belo_horizonte_trip.csv",
#                  guess_max = 100000)
# quality_check(trip_belo_horizonte)
# trip_summary$Belo_Horizonte <- value
# 
# trip_mexico_city <- read_csv("../../data/local/mexico_city/mexico_city_trip.csv",
#                  guess_max = 100000)
# quality_check(trip_mexico_city)
# trip_summary$Mexico <- value
# 
# trip_bogota <- read_csv("../../data/local/bogota/bogota_trips.csv",
#                  guess_max = 100000)
# quality_check(trip_bogota)
# trip_summary$Bogota <- value
# 
# trip_santiago <- read_csv("../../data/local/santiago/santiago_trip.csv",
#                  guess_max = 100000)
# quality_check(trip_santiago)
# trip_summary$Santiago <- value
# 
# trip_vizag <- read_csv("../../data/local/vizag/vizag_trip.csv",
#                  guess_max = 100000)
# quality_check(trip_vizag)
# trip_summary$Visakhapatnam <- value
# 
# trip_delhi <- read_csv("../../data/local/delhi/delhi_trip.csv",
#                  guess_max = 100000)
# quality_check(trip_delhi)
# trip_summary$Delhi <- value
# 
# trip_bangalore <- read_csv("../../data/local/bangalore/bangalore_trip.csv",
#                  guess_max = 100000)
# quality_check(trip_bangalore)
# trip_summary$Bangalore <- value
# 
# trip_accra <- read_csv("../../data/local/accra/accra_trip.csv",
#                  guess_max = 100000)
# quality_check(trip_accra)
# trip_summary$Accra <- value
# 
# trip_cape_town <- read_csv("../../data/local/cape_town/cape_town_trip.csv",
#                  guess_max = 100000)
# quality_check(trip_cape_town)
# trip_summary$Cape_Town <- value
#

@@

```{r, include = TRUE,  echo= FALSE, results='asis'}
rownames(trip_summary)
trip_summary[50:61,]
```
